---
title: "Cross_Validation"
output: html_document
date: '2022-04-21'
---

```{r}
library(tidyverse)
library(caret)
```


```{r}
iris %>%
  ggplot(aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  theme_bw()
```

```{r}
trControl <- trainControl(method = "cv",
number = 5)
```

```{r}
mod_iris = iris %>%
select(-contains('Sepal'))
```


```{r}
fit <- train(Species ~ ., ## Species is the response variable
method = "knn", ## Machine Learning Algorithm
tuneGrid = expand.grid(k = 1:10), ## Number of different neighbors
trControl = trControl, ## Define the type of cross validation
metric = "Accuracy", ## The metric for performance
data = iris ## The data set
)

fit
```

#Question 1: Higher numbers of neighbors caused the highest level of accuracy.

#Question 2: The k value which had the highest level of accuracy is 22, however this does change as from test to test.

#Question 3: The k value that had the highest level of accuracy is 10, however this does change as from test to test.

#Question 4: The k value that has the highest level of accuracy is 5, however this does change as from test to test.

