---
title: "One_Way_ANOVA_Part1"
output: html_document
date: '2022-04-05'
---

##Question 1: Does the amount of octane (87, 89,91) present in gasoline affect gas mileage?

##Question 2: The null hypothesis means that the gas mileage is the same across the differing amounts of octane.



```{r}
library(readxl)
library(tidyverse)
library(broom)
```


```{r}

sheet_names_years = c("1980","1990","2000","2010")

#function declaration
read_in_sheet_fun = function(sheet_name){
  #uses sheet name to decide what sheet to make pet_names as
  tmp_df = read_xlsx("pitcher_data.xlsx", sheet_name) %>% 
    mutate(year = sheet_name) %>% 
    filter(Lg != 'MLB') %>%  ## Remove data in which the pitcher played for more than 2 teams
    distinct(Name,max(G),.keep_all = TRUE) ## Find the unique players based on the year
  
  #returns pet names
  return(tmp_df)
}


#selects each sheet by name
years_pitch_lst = map(sheet_names_years,read_in_sheet_fun)


#Names each vector in list
names(years_pitch_lst) = sheet_names_years

years_pitch_df = bind_rows(years_pitch_lst,.id = 'Year') %>% 
  mutate(year = as.numeric(year)) %>% 
  drop_na()

colnames(years_pitch_df)[c(9,29,37)] = c('W_L_perc','ERA_plus','SO_div_W')
```



##Question 3: The null hypothesis is that the year that the pitchers played wouuld not affect the FIP variable. 


```{r}
years_pitch_df = years_pitch_df %>% 
  mutate(Year = as.factor(Year))
```


```{r}
years_pitch_df %>%  
  ggplot(aes(x = Year, y = FIP)) +
  geom_boxplot() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Year', y = 'FIP', title = 'Box Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```

```{r}
years_pitch_df %>%  
  ggplot(aes(x = Year, y = FIP)) +
  geom_violin() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Year', y = 'FIP', title = 'Violin Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```

##PART 2


```{r}
summary_pitch_df = years_pitch_df %>% 
  group_by(Year) %>% 
  summarise(sample_size = n(),
            mean_FIP = mean(FIP,na.rm = TRUE),
            sd_FIP = sd(FIP,na.rm = TRUE))

summary_pitch_df
```

##Question 1:The mean measures the average FIP, meaning the center or average of the numbers.

##Question 2: Standard deviation measures the variability, or average deviation of the data


```{r}
ratio_anova = sd(summary_pitch_df$mean_FIP) / mean(summary_pitch_df$sd_FIP)
ratio_anova
```
```{r}
max(summary_pitch_df$sd_FIP)/min(summary_pitch_df$sd_FIP)
```

##PART 3

```{r}
model1 = aov(FIP ~ Year, years_pitch_df)
tidy(model1)
```

```{r}
K = 3
n = 32

df_groups = K - 1 
df_residuals = n - K
```

```{r}
overall_mean = mean(years_pitch_df$FIP, na.rm = TRUE)

SS_groups_df = years_pitch_df %>% 
  group_by(Year) %>% 
  summarise(group_means = mean(FIP,na.rm = TRUE), group_sample_size = n()) %>% 
  mutate(mean_diff = (group_means - overall_mean)) %>% 
  mutate(mean_diffsq = (mean_diff)^2) %>% 
  mutate(sam_mean_diffsq = (group_sample_size)* mean_diffsq )
  
(SS_groups = sum(SS_groups_df$sam_mean_diffsq))
```

```{r}
SS_residuals_df = years_pitch_df %>% 
  group_by(Year) %>% 
  summarise(sd_group = sd(FIP, na.rm = TRUE), group_sample_size = n()) %>% 
  mutate(sp2 =  (group_sample_size - 1)*(sd_group^2))

(SS_residuals = sum(SS_residuals_df$sp2))
```
```{r}
(MS_groups = SS_groups/df_groups)
```

```{r}
(MS_residual = SS_residuals/df_residuals)

```

```{r}
(TS = MS_groups / MS_residual)
```
##P Value
```{r}
1 -  pf(TS, df_groups,df_residuals)
```

