---
title: "Two-Way ANOVA"
output: html_document
date: '2022-04-11'
---

#Question 1: An example where Two-Way ANOVA could be implemented is: Does the amount of octane in fuel (87, 89, 91) or type of transmission(automatic or manual) affect 0-60 accelaration times.

#Octane amount(categorical), Transmission type(categorical binary), accelaration time(quantitative)

#Question 2: The null hypothesis for the above example is if the population means are the same for amount of octane, type of transmission and when there is no interaction effect between the two.

```{r}
library(tidyverse)
library(readxl)
library(ggpubr)
```

```{r}



sheet_names_years = c("1980","1990","2000","2010")

#function declaration
read_in_sheet_fun = function(sheet_name){
  #uses sheet name to decide what sheet to make pet_names as
  tmp_df = read_xlsx("pitcher_data.xlsx", sheet_name) %>% 
    mutate(year = sheet_name) %>% 
    filter(Lg != 'MLB') %>%  ## Remove data in which the pitcher played for more than 2 teams
    distinct(Name,max(G),.keep_all = TRUE) ## Find the unique players based on the year
  
  #returns pet names
  return(tmp_df)
}


#selects each sheet by name
years_pitch_lst = map(sheet_names_years,read_in_sheet_fun)


#Names each vector in list
names(years_pitch_lst) = sheet_names_years

years_pitch_df = bind_rows(years_pitch_lst,.id = 'Year') %>% 
  mutate(year = as.numeric(year)) %>% 
  drop_na()

colnames(years_pitch_df)[c(9,29,37)] = c('W_L_perc','ERA_plus','SO_div_W')
```





```{r}
mod_pitcher_df = years_pitch_df %>% 
  mutate(Year = as.factor(Year))
```


```{r}
ggboxplot(mod_pitcher_df, x = "Year", y = "FIP", color = "Lg",
          palette = c("#00AFBB", "#E7B800")) +
  labs(x = 'Year', y = 'FIP', title = 'Box Plot for One-Way ANOVA with means') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```

